Security Properties for Stack Safety

### 2021-05-16 short/main.tex
Paragraph 4 tweaked

Our threat model is very strong, allowing the attacker (i.e., the callee) to
execute arbitrary code, including code that might attempt to smash
the stack to disrupt the program's control flow.
Our stack safety properties demand that, even in the presence of such
attackers, confidentiality and integrity must
still apply to data in suspended stack frames until the callee returns.
The question then arises:
what constitutes a return in this setting? It is not obvious, since our
setting is a concrete, low-level ISA where the same opcode might sometimes
be used to return from a call and sometimes for other purposes.
Our solution is to associate with each call a corresponding predicate on states,
its ``return target,''
which holds on the states that would follow a well-behaved return.
Whether or not a callee executes a return instruction,
we only recognize it returning only when it reaches a return target.
So the caller is protected until then, even if the callee is
executing instructions outside of its normal footprint.

>>>>

Our threat model is very strong, allowing the attacker (i.e., the callee) to
execute arbitrary code, including code that might attempt to smash
the stack to disrupt the program's control flow.
Our stack safety properties demand that, even in the presence of such
attackers, confidentiality and integrity must
still apply to data in suspended stack frames until the callee returns.
The question then arises:
what constitutes a return in this setting? It is not obvious, since our
setting is a concrete, low-level ISA where the same opcode might sometimes
be used to return from a call and sometimes for other purposes.
Our solution is to associate with each call a corresponding predicate on states,
its ``return target,''
which defines what it means for that call to truly return: the program counter
must be at the next instruction, and the stack pointer restored to its original
value.
So the caller is protected until its return target is reached, even if the callee is
executing instructions outside of its normal footprint.
